Manuscript_Github_Pchabaudi_calculateTPM

### 2022-07-21 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_calculateTPM.Rmd
Save the tpm files

```{r clean_up_and_average}
chab_tpm_avg.df <- reshape2::melt(chab_tpm.df, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  reshape2::dcast(Geneid ~ stage)
```

```{r save}
write_csv(twentyfour_rMT,
          file = 'Pchabaudi_TPM_allBioReps.csv')

write_csv(twentyfour_rMT_avg,
          file = 'Pchabaudi_TPM_average.csv')
```

>>>>

```{r clean_up_and_average}
chab_tpm_avg_nopseudo.df <- reshape2::melt(chab_tpm_rescale_nopseudo, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  reshape2::dcast(Geneid ~ stage)
```

```{r save}
write_csv(chab_tpm.df,
          file = 'data/Pchabaudi_TPM_all_withPseudo.csv')

write_csv(chab_tpm_rescale_nopseudo,
          file = 'data/Pchabaudi_TPM_all.csv')

write_csv(chab_tpm_avg_nopseudo.df,
          file = 'data/Pchabaudi_TPM_average.csv')
```
